 \documentclass[10pt]{resume}
\usepackage[scaled]{berasans}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
%------------------------------------------------

\name{Vishnu Shon}
\links{\href{mailto:vshon447@gmail.com}{vshon447@gmail.com}}
\links{\href{https://github.com/VisShon}{Github}}
\links{\href{https://www.linkedin.com/in/visshon/}{LinkedIn}}

%----------------------------------------------------------------------------------------
\begin{document}
    %	WORK EXPERIENCE SECTION
    \begin{rSection}{Work Experience}
        %------------------------------------------------

        \begin{rSubsection}{StayBook | Product Lead}{August 2022 - September 2023}
            \item Spearheaded the development of the highly efficient Booking API \vspace{-0.3em} micro-service and data delivery integration with Google hotel center, serving customers for 200+ hotels , garnering a 25\% increase in digital revenue.
            \item Architected CDN caching for static content and  Load  \vspace{-0.3em} balancing for traffic optimization using Google cloud load balancing, reducing LCP load times from 5s to <2.5s.
            \item Critically increased product sales by targeting google \vspace{-0.3em} insights and optimizing SEO resulting in 20,000 daily site visits. 
        \end{rSubsection}

        %------------------------------------------------
        
        \begin{rSubsection}{Mathworks | EDG Intern}{May 2023 - July 2023}
            \item Implemented UI Testing for Simulink VR Editor, revamping 
            \vspace{-0.3em} 7 test module for the newer JS based virtual world editor, and creating helper classes for interactive test cases. 
            \item Orchestrated the adoption of a class-based testing framework, leading to a 30\% improvement in software quality. 
            \item Bashed the SL3D editor module for understanding test needs, \vspace{-0.3em} identified 5 severe bugs in the new virtual world editor, which were raised for the upcoming releases, this helped writing new tests for the VR Editor.

        \end{rSubsection}

        %------------------------------------------------
    
        \begin{rSubsection}{Government of India | Full Stack Developer}{March 2023 - February 2023}
            \item Implemented a crucial Proof of Concept for a government \vspace{-0.3em} internal software, collaborating with 2 senior  officials and a PhD team of 5, from IIT Bombay. 
            \item Led the integration of the backend with \vspace{-0.3em} GeoServer, using PostGIS and OSM api, incorporating satellite data with a composable React UI.
            \item Pionnered authentication using the government SSO servers, setting the solid groundwork for future deployment.
        \end{rSubsection}
    
        %------------------------------------------------
    
    	\begin{rSubsection}{Respct | Founding Member}{December 2021 - July 2022}
                \item Achieved a milestone with successful pre-seed and seed \href{https://inc42.com/buzz/meet-the-31-web3-startups-that-are-part-of-first-cohort-of-polygonleap-2021/}{funding} of over \$1M, participating in Tachyon 22 \vspace{-0.3em} accelerator program. Expanded product visibility and usability through the USM Metaverse integration.
               \item Orchestrated the conceptualization and implementation \vspace{-0.3em} of product features, utilising NextJS and EthersJs to craft an immersive user interface and experience, leading to a 50\% surge in user adoption.
                \item Proposed an integrative approach for embedding Respct \vspace{-0.3em} inside the USM Metaverse, managing a multidisciplinary team of developers and designers. 
    	\end{rSubsection}
    
    \end{rSection}
    
    %	PROJECTS SECTION
    \begin{rSection}{Projects}
            \begin{rSubsection}{Escrow Based Payment Management Platform}            {\href{https://github.com/RevereLabs}{Github}}
                \item Led the development of an escrow payment platform \vspace{-0.3em} leveraging NextJS, EthersJS, AWS, and Moralis SDK, bagging a \$ 2000 win in Polygon BuidlIt Hackathon 2022. 
                \item Championed web 3 development and market study buoyed \vspace{-0.3em} by a comprehensive 3-month States DAO mentorship, Supervising platform business logic and protocol integration.
    	\end{rSubsection}
         %------------------------------------------------
        
        \begin{rSubsection}{Interview Scheduling Sofrware}
            {\href{https://github.com/VisShon/InterviewLink}{Github}}
                \item spearheaded the implementation of a robust platform \vspace{-0.3em}using a Microservices Architecture, incorporating NextJs for the application and ExpressJs for scheduling server and integrating technologies like Neo4j, GraphQL, Apollo and Google NLP API.
                \item Established CI/CD pipeline with Google Cloud Run and GBuild triggers, Implemented Cypress for rigorous UI testing and scalable deployment.
    	\end{rSubsection}

        %------------------------------------------------
         
         \begin{rSubsection}{Decentralised Journalism Platform}
            {\href{https://github.com/0xFethr}{Github}}
                \item Led the development of a decentralised journalism \vspace{-0.3em}platform with NextJs, EthersJs, GraphQl, and Ceramic Network, reduced content censorship risks by leveraging blockchain technology. 
                \item Developed features like faucet via Wagmi, subscription pipeline via Superfluid, and secure identities with Ceramic DID. 
                \item Secured the runner-up spot at the IGDTUW Devacation \vspace{-0.3em} Hackathon by leading a team of 5 in developing an innovative project with a credible use of web3.
        \end{rSubsection}

        %------------------------------------------------
    
        \begin{rSubsection}{Social Trading Platform}
        {\href{https://github.com/AlkyneFi}{Github}}
            \item Developed and designed a social DeFi platform at \vspace{-0.3em} ETHIndia 2022, leveraging NextJs, EthersJs, and Uniswap API for robust frontend development. 
            \item Amalgamated third-party protocols such as Push protocol, Filecoin, and Covalent API, earning a collective \$1700+ accolade.
        \end{rSubsection}
    
        %------------------------------------------------
    
    \end{rSection}

    %	SKILLS SECTION
    \begin{rSection}{Skills}
        \begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
            Computer Languages & JavaScript, TypeScript, SQL, GraphQL, Python, HTML, CSS, Java, C \\
            Platforms \& APIs & Google Cloud Platform, Firebase, Moralis, Infura, Sanity, Docker, Moz \\
            Databases & MySQL, PostgreSQL, MongoDB, Redis Cache, Neo4j, Ceramic Compose, Firestore \\
            Libraries/Frameworks & NEXTJs, ReactJs, ReactNative, ExpressJs, NodeJs, EthersJs, Apollo,  Redux, WebSockets \\
        \end{tabular}
    \end{rSection}
    
    %  AWARDS and POSITIONS SECTION
    \begin{rSection}{Awards}
    
        \begin{rOthers}{\textbf{Bounty Winner}, Eth India Hackathon India’s Biggest Web3 Hackathon}{December 2022}
        \end{rOthers}
    
        %------------------------------------------------
    
        \begin{rOthers}{\textbf{Pool Winner}, Polygon Buidlit Hackathon}
        {September 2022}
        \end{rOthers}
     
    \end{rSection}

    %  POSITION OF RESPONSIBILITY SECTION
    \begin{rSection}{Leadership and Community}
    
        \begin{rOthers}{\textbf{Club Coordinator}, Google Developer Student Club IIITD}{July 2023}
        \end{rOthers}
    
        %------------------------------------------------
    
        \begin{rOthers}{\textbf{Convener}, 1Pixel Design Conference}
        {January 2023}
        \end{rOthers}
     
    \end{rSection}
    
    %	EDUCATION SECTION
    \begin{rSection}{Education}
        \textbf{Indraprastha Institute of Information Technology, Delhi} \hfill \textit{January 2020 - July 2024} \\ 
        B.Tech (Computer Science \& Design) \\
    \end{rSection}

\end{document}