 \documentclass[10pt]{resume}
\usepackage[scaled]{berasans}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
%------------------------------------------------

\name{Vishnu Shon}
\links{\href{mailto:vshon447@gmail.com}{vshon447@gmail.com}}
\links{\href{https://github.com/VisShon}{Github}}
\links{\href{https://www.linkedin.com/in/vishnu-shon-079007202/}{LinkedIn}}

%----------------------------------------------------------------------------------------
\begin{document}
    %	WORK EXPERIENCE SECTION
    \begin{rSection}{Work Experience}
        \begin{rSubsection}{Mathworks | EDG Intern}{May 2023 - July 2023}
            \item Revamped existing function-based UI tests for the Simulink 3D World Editor into a more effective class-based framework. 
            \item Orchestrated the adoption of a cutting-edge class-based testing framework, leading to a 30\% improvement in software quality for the upcoming software release. 
            \item Enhanced test quality by 30\%, gained valuable insights on client relationships and ensured a top-quality product.
        \end{rSubsection}
    
        %------------------------------------------------

        \begin{rSubsection}{StayBook | DevOps Developer}{February 2023 - October 2023}
            \item Spearheaded the development of CI/CD pipelines for booking engine and API services while also crafting an ARI server for integration with Google Hotel Centre, increasing the bookings by 40\%. 
            \item Implemented Cloud Storage Buckets and Cloud CDN for static data management and Cloud Load Balancers for product traffic optimization. Leveraged tools such as TypeScript, NextJs, Firestore, Google Cloud Platform, Docker, and Google Cloud Run.
            \item Augmented product efficiency and performance led to a robust API booking service strategy resulting in a 30\% reduction in load times and improved overall platform performance.
        \end{rSubsection}

        %------------------------------------------------
    
        \begin{rSubsection}{Government of India (D.R.D.O) | Full Stack Developer}{March 2023 - February 2023}
            \item Architected a crucial Proof of Concept for internal software, collaborating with government officials and PhD team from IIT Bombay, delivering an innovative solution. 
            \item Harnessed Post GIS and OSM API to integrate an Express backend with the GeoServer, incorporating satellite data.
            \item Delivered the platform for setting the solid groundwork for an upcoming government project.
        \end{rSubsection}
    
        %------------------------------------------------
    
    	\begin{rSubsection}{Respct | Founding Member}{December 2021 - July 2022}
                \item Achieved a milestone with successful pre-seed and seed \href{https://inc42.com/buzz/meet-the-31-web3-startups-that-are-part-of-first-cohort-of-polygonleap-2021/}{funding} of over \$1M, participating in Tachyon 22 accelerator program. Expanded product visibility and usability through the Metaverse integration.
                \item Played a pivotal role in devising business plans and developing the application utilizing NextJS, Figma and EthersJs to build the user interface and experience.  
                \item Proposed an integrative approach for embedding Respct inside the USM Metaverse, managing a multidisciplinary team of developers and designers. 
    	\end{rSubsection}
    
    \end{rSection}
    
    %	PROJECTS SECTION
    \begin{rSection}{Projects}
    
            \begin{rSubsection}{Escrow Based Payment Management Platform}                   {\href{https://github.com/RevereLabs}{Github}}
                \item Led the development of an escrow payment platform leveraging NextJS, EthersJS, AWS, and Moralis SDK, bagging a \$ 2000 win in Polygon BuidlIt Hackathon 2022. 
                \item Championed web 3 development and market study buoyed by a comprehensive 3-month States DAO mentorship, Supervised platform design and protocol integration.
    	\end{rSubsection}

        %------------------------------------------------
         
         \begin{rSubsection}{Decentralized Journalism Platform}
            {\href{https://github.com/0xFethr}{Github}}
                \item Led the development of a decentralized journalism platform with NextJs, EthersJs, GraphQl, and Ceramic Network. 
                \item Developed features like faucet via Wagmi, subscription pipeline via Superfluid, and secure identities with Ceramic DID. 
                \item This innovative project secured the runner-up spot at the IGDTUW Devacation Hackathon.
        \end{rSubsection}
    
        %------------------------------------------------
    
            \begin{rSubsection}{Social Trading Platform}
            {\href{https://github.com/AlkyneFi}{Github}}
                \item Developed and designed a social DeFi platform at ETHIndia 2022, leveraging NextJs, EthersJs, and Uniswap API for robust frontend development. 
                \item Amalgamated third-party protocols such as Push protocol, Filecoin, and Covalent API, earning a collective \$1700+ accolade.
    	\end{rSubsection}
    
        %------------------------------------------------
    
    	\begin{rSubsection}{Event Management Application}
            {\href{https://github.com/VisShon/Vantage}{Github}}
                \item Deployed an advanced event management platform, incorporating technologies like NextJS, Neo4j, GraphQL, and Apollo client. 
                \item Established private routing and middleware to ensure secure access and efficient navigation. 
                \item Recognized as the 'Best in Usable Security' by a highly regarded IIITD professor, highlighting the exceptional quality and impact.
    	\end{rSubsection}
    
    \end{rSection}

    %	SKILLS SECTION
    \begin{rSection}{Skills}
        \begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
            Computer Languages & JavaScript, TypeScript, SQL, GraphQL, Python, HTML, CSS, Java, C \\
            Platforms \& APIs & Google Cloud Platform, Firebase, Moralis, Infura, Sanity, Docker, Moz \\
            Databases & MySQL, PostgreSQL, MongoDB, Redis Cache, Neo4j, Ceramic Compose, Firestore \\
            Libraries/Frameworks & NEXTJs, ReactJs, ReactNative, ExpressJs, NodeJs, EthersJs, Apollo,  Redux, WebSockets \\
        \end{tabular}
    \end{rSection}
    
    %  AWARDS and POSITIONS SECTION
    \begin{rSection}{Awards}
    
        \begin{rOthers}{\textbf{Bounty Winner}, Eth India Hackathon India’s Biggest Web3 Hackathon}{December 2022}
        \end{rOthers}
    
        %------------------------------------------------
    
        \begin{rOthers}{\textbf{Pool Winner}, Polygon Buidlit Hackathon}
        {September 2022}
        \end{rOthers}
     
    \end{rSection}

    %  POSITION OF RESPONSIBILITY SECTION
    \begin{rSection}{Leadership and Community}
    
        \begin{rOthers}{\textbf{Club Coordinator}, Google Developer Student Club IIITD}{July 2023}
        \end{rOthers}
    
        %------------------------------------------------
    
        \begin{rOthers}{\textbf{Convener}, 1Pixel Design Conference}
        {January 2023}
        \end{rOthers}
     
    \end{rSection}
    
    %	EDUCATION SECTION
    \begin{rSection}{Education}
        \textbf{Indraprastha Institute of Information Technology, Delhi} \hfill \textit{January 2020 - July 2024} \\ 
        B.Tech (Computer Science \& Design) \\
    \end{rSection}

\end{document}